Predictors of frog survival following translocations - analyses

### 2022-10-13 code/translocation_survival_analysis.Rmd
Add text describing motivation for Model 2

# Model 2: Survival of frogs from first translocation as predictor of survival in subsequent translocations
## Load packages

>>>>

# Model 2: Survival of frogs from first translocation as predictor of survival in subsequent translocations

This analysis explores the results shown in translocation_survival_exploratory.Rmd (code chunk name = "frog-survival-by-site"). This plot shows frog survival of all translocations grouped by site, and indicates that survival is highly variable across sites, but repeatable within a site. This analysis quantifies the association between survival in the first translocation and survival in subsequent translocations.
